Precision calculations of the cosmic shear power spectrum projection

### 2017-02-02 limber2.tex
Reshuffle - moved old files from the comment paper to a new directory

\author[M.~Kilbinger et~al.]
 {
  \parbox[h]{\textwidth}
  {
      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
      Catherine Heymans,
      Peter Schneider,
      Shahab Joudaki,
      Marika Asgari,
      and other members of CFHTLenS and KiDS
      $\ldots$,
  }
  % 
  \vspace*{10pt} \\
  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
           France \\
 }

@@

\input abbr-journals

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{P_kappa_limber_comp}
      \includegraphics{P_kappa_limber_delta}
    }
  \end{center}

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{xi_p_comp}
      \includegraphics{xi_m_comp}
    }
  \end{center}

@@

  \begin{center}
    \resizebox{0.9\hsize}{!}{
      \includegraphics{P_kappa_limber_delta_Rijt}
    }
  \end{center}

>>>>

\author[M.~Kilbinger et~al.]
 {
  \parbox[h]{\textwidth}
  {
      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
      %Catherine Heymans,
      %Peter Schneider,
      %Shahab Joudaki,
      %Marika Asgari,   % note that we'll worry about order at the end - Marika and Shahab put a lot of work into the comment paper, so we might just want to go alpha
      and other members of CFHTLenS and KiDS
      $\ldots$,
  }
  % 
  \vspace*{10pt} \\
  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
           France \\
 }

@@

%\input abbr-journals

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_comp}
      \includegraphics{figures/P_kappa_limber_delta}
    }
  \end{center}

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/xi_p_comp}
      \includegraphics{figures/xi_m_comp}
    }
  \end{center}

@@

  \begin{center}
    \resizebox{0.9\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_delta_Rijt}
    }
  \end{center}

### 2017-02-02 original_comment_paper/conclusion.tex
Reshuffle - moved old files from the comment paper to a new directory

\section{Acknowledgements}
We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi and Adam Amara for useful discussions during the collection of these comments.

>>>>

\section{Acknowledgements}
We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for useful discussions during the collection of these comments.
